Reasonably Programmable Literal Notation: Supplemental Material

### 2018-07-16 icfp18/supplement/icfp18-supplement.tex
changed subsubsection formatting per publisher request

\usepackage[colorlinks=true,allcolors=Blue,backref,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
pdfborder={0 0 0},  %removes outlines around hyper links in online display
]{hyperref}

@@

\usepackage{mathtools}
\usepackage{ stmaryrd }
\usepackage[numbers,sort]{natbib}

@@

\abstract{
This report presents a complete technical account of the formal system that was described in the accompanying paper, as well as more details on the quasiquotation TLM.
}

@@

%\arpasupport{fox}
\support{This work was
supported in part by AFRL and DARPA under agreement \#FA8750-16-2-0042;
 by the NSA under lablet contract \#H98230-14-C-0140.}
% \authorsupport{The author holds a Froboz Gradual Fellowship.}

@@

\bibliographystyle{plainnat}
\bibliography{../../../../papers/research} %your bib file

>>>>

\usepackage[colorlinks=true,allcolors=Blue,pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
pdfborder={0 0 0},  %removes outlines around hyper links in online display
]{hyperref}

@@

\usepackage{mathtools}
\usepackage{ stmaryrd }
\usepackage[numbers]{natbib}

@@

\abstract{
This report presents a complete technical account of the formal system that was described in the accompanying paper \cite{tlms-icfp18}, as well as more details on the quasiquotation TLM.
}

@@

%\arpasupport{fox}
\support{This work was
supported in part by AFRL and DARPA under agreement \#FA8750-16-2-0042 and 
 by the NSA under lablet contract \#H98230-14-C-0140.}
% \authorsupport{The author holds a Froboz Gradual Fellowship.}

@@

\bibliographystyle{plainnat}
\bibliography{../research} %your bib file
